### 2012-11-13 doc/progress_plan/report.tex
Added talk about why goodreads and citeulike aren't great for content indexing

>>>>

These systems have the ability to make recommendations to the user without
requiring specific keywords or search terms. They are able to do this by
learning the user's profile and taking into account the preferences of their
'friends' and their browsing history. However, the above-named systems do not
take into account the content of the paper or book. They only deal with
metadata as can be seen in Figure \ref{fig:social_searches}. This means that
important discriminatory information that could be contained within the actual
document content is overlooked completely. Partridge will analyse documents on
a sentence-by-sentence and possibly word-by-word basis, thereby taking account
of any embedded information that could be missed by these social metadata
systems.

\begin{figure}[!hbt]
        \centering
        \begin{subfigure}[b]{0.50\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images/goodreads_search.png}
                \caption{Goodreads advanced search page}
                \label{fig:goodreads_search}
        \end{subfigure}%
        \begin{subfigure}[b]{0.50\textwidth}
                \centering
                \includegraphics[width=\textwidth]{images/citeulike_search.png}
                \caption{CiteULike advanced search options}
                \label{fig:citeulike_search}
        \end{subfigure}

        \caption{Goodreads and citeulike search only deal with metadata.}
        \label{fig:social_searches}
\end{figure}
